Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-10 write-ups/PLDI/paper.tex

>>>>

\begin{lstlisting}
kernel work_stealing(global Task *pools, const int num_pools) {
  while (more_work(pools)) {
    int pool_id = get_group_id() % num_pools;
    Task *t = pop_or_steal(pools, pool_id, num_pools);
    if (t) {
      // task processing may create more work
      process_task(t, pools, pool_id);
    }
  }
}
\end{lstlisting}

\caption{Cooperative version of work stealing: the number of workpools
must be explicitely passed as arguments since the number of workgroups
is not a constant anymore}\label{fig:workstealing-cooperative}
\end{figure}
